### 2022-06-16 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_betacov_mapping@3386f7c9b624ab21772c3543697456665d27c11e 🚀

Based on the previous result, we extracted the yellow component of the
risk map (TP add methods), to provide a single measure of risk varying
between 0 and 1. This measure is presented in fig.~\ref{fig:risk}.
However, this maps the potential risk, which must be weighed by the
potential for contacts with humans. As a proxy for this measure, we used
the proportion of build/urban land from the EarthEnv dataset: this is a
reasonable proxy for the density of humans per unit area, which
increases the probability of pathogen spread more widely (Hazarie et al.
2021). Since human activity is required to amplify the frequency of
virus encounters and thus create areas of viral amplification, mapping
the potential risk against measures of land use is required to generate
a more actionable assessment of risk. This map is presented in
fig.~\ref{fig:compound}. Most of South America and Europe are at low
risk, as although densely populated, settlements tend to be in areas
with lower potential risk. However, this mapping reveals that South-East
Asia, the Indian subcontinent, and parts of sub-Saharan Africa, are at
high risk due to the overlap between built areas and bat communities
representing more opportunities for cross-species transmission of
betacoronaviruses. In looking for the origins of SARS in China, Xu et
al. (2004) present serological evidence that strongest human-animal
contact results in higher risk of virus exposure, regardless of the
animal species, but that different types of contact had different
impacts. Ideally, finer-grained information about human activity (rather
than human presence through anthropisation) could allow to partition
this risk further.

>>>>

Based on the previous result, we extracted the risk component from the
composite map (see Methods), to provide a single measure of risk varying
between 0 and 1. This measure is presented in fig.~\ref{fig:risk}.
However, this maps the potential risk, which must be weighed by the
potential for contacts with humans. As a proxy for this measure, we used
the proportion of build/urban land from the EarthEnv dataset: this is a
reasonable proxy for the density of humans per unit area, which
increases the probability of pathogen spread more widely (Hazarie et al.
2021). Since human activity is required to amplify the frequency of
virus encounters and thus create areas of viral amplification, mapping
the potential risk against measures of land use is required to generate
a more actionable assessment of risk. This map is presented in
fig.~\ref{fig:compound}. Most of South America and Europe are at low
risk, as although densely populated, settlements tend to be in areas
with lower potential risk. However, this mapping reveals that South-East
Asia, the Indian subcontinent, and parts of sub-Saharan Africa, are at
high risk due to the overlap between built areas and bat communities
representing more opportunities for cross-species transmission of
betacoronaviruses. In looking for the origins of SARS in China, Xu et
al. (2004) present serological evidence that strongest human-animal
contact results in higher risk of virus exposure, regardless of the
animal species, but that different types of contact had different
impacts. Ideally, finer-grained information about human activity (rather
than human presence through anthropisation) could allow to partition
this risk further.
